### 2019-04-22 dantzig_selector/report/1_introduction.tex
Set & correct simulation variables
Kronecker product identity proof

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\Mb {R}^N} is over field \m {\Mb {R}}, and that on \m {\Mb {C}^N} is over field \m {\Mb {C}}.
We use \m {\Mb {K}} to refer to either \m {\Mb {R}} or \m {\Mb {C}}.
Not to avoid confusion, we call the Hilbert space \m {\Mb {K}^N} over \m {\Mb {K}} to be \m {\Mb {V}_{\Mb {K}} \SB {N}}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\Mb {M}_{\Mb {K}} \SB {M,N}}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
Particularly, \m {\V {u}_n} is the \m {n}-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \Mb {N}} is much larger than the number of measurements \m {N_m \in \Mb {N}}, namely,
%
\Disp {
\NC N_p \gg N_m \NR
}
%
In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

\Result
{Definition}
{
\m {x \in \Mb {V}_{\Mb {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\Mc {A}}, \m {s <N_m}, if there is \m {\Mc {A} \subset T \RB {N_m}} such that
%
\Disp { 
\NC x_{T\SB {N} -\Mc {A}}
=\NC \V {0} \NR
}
with
\Disp { 
\NC \# \Mc {A} \leq s. \NR
}
That is, only at most \m {s} components of \m {x} is nonzero.
}

\Result
{Definition}
{
Consider \m {P \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N_p}}, for all \m {\Mc {T} \subset T\SB {N_m}} with \m {\#\{\Mc {T} \} \leq s},
%
\Disp {
\NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
\NC \leq \NC \VNm {P_{\Mc {T}} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
}
}

@@

Now, consider a linear transformation with noise corruption,
%
\Disp {
\NC \V {y} =\M {P} \V {h} + \V {z} \NR
}
%
where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {h} when, in addition to insufficient observations, there are too few observations?

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {P} \in \Mb {V}_\Mb {R} \SB {N_m, N_p}}, \m {\V {y} \in \Mb {V}_\Mb {R} \SB {N_m}}.
\item Find \m {\V {h} \in \Mb {V}_\Mb {R} \SB {N_m}} by
\Disp {
\NC \V {h}
= \NC \startcases
\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \gamma \NR
\stopcases \NR
}
\item Output \m {\V {h}}.
}

@@

\Result
{Theorem}
{
Let each entry of random matrix \m {P \in \Mb {M}_\Mb {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
Then, with \m {0 <\epsilon <1},
%
\Disp {
\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \epsilon \VNm {h} _2^2} \NR
\NC \leq \NC 2 \exp \SB {-n \RB {\epsilon^2/4 -\epsilon^3/6} } \NR
}
}

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m {0 <\d <1},
%
\Disp {
\NC M \geq 16s \log \RB {N/\d} \NR
}
%
Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
}

@@

For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is
%
\Disp {
\NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
}
%

\Result
{Definition}
{
Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {K}^{NM}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}.
}

\Result
{Definition.}
{
For \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}} and \m {\Mr {vec} \SB {A} \in \Mb {M}_{\Mb {K}} \SB {N,M}}
Define the Kronecker product \m {\Mr {vec} \SB {A} \in \Mb {K}^{nm}} 
}

With (), scholars often exploit the relation
%
\Disp {
\NC \Mr {vec} \SB {Y}
=\SB {\RB {F^\Adj} \otimes W} \Mr {vec} \RB {\M {H}} \NR
}
%

>>>>

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \m {\Mb {R}^N} is over field \m {\Mb {R}}, and that on \m {\Mb {C}^N} is over field \m {\Mb {C}}.
We use \m {\Mb {K}} to refer to either \m {\Mb {R}} or \m {\Mb {C}}.
Not to avoid confusion, we call the Hilbert space \m {\Mb {K}^N} over \m {\Mb {K}} to be \m {\Mb {V}_{\Mb {K}} \SB {N}}.
We also call the collection of \m {M} by \m {N} matrices to be \m {\Mb {M}_{\Mb {K}} \SB {M,N}}, and its role as linear transformation is understood.
Inner product of \m {\V {a}} and \m {\V {b}} is denoted as \m {\IP { \V {a}, \V {b} }}.
Slightly abusing notation, we denote as \m {\V {a} \DB {n}} the \m {n}-th component of \m {\V {a}}, and denote as \m {\V {A} \DB {m,n}} the \m {\DB {m,n}}-entry of \m {\V {A}}
To better correspond to the pseudo code, the numbering of both vector and matrix entries are zero-based, that is, numbered from \m {0,1,2,\dots}.
Especially when manipulating the indices, but also in the main proof of DS bound, we will encounter the modulo as operation, namely the remainder of \m {m} divided by \m {n}, with \m {m, n \geq 0}, and we use the capital \m {m\; \rm{Mod}\; n} to denote that number.
And we denote \m {\V {u}_n} to be the \m {n}-th unit vector in the Cartesian coordinates, whose numbering is also zero-based.
\m {\VNm {\V {a}} _p} denotes the \m {\ell_p}-norm of vector \m {\V {a}}.
Recall that \m {\ell_\infty}-norm is the maximum-magnitude norm.

@@

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \m {N_p \in \Mb {N}} is much larger than the number of measurements \m {N_m \in \Mb {N}}, namely,

\Disp {
\NC N_p \gg N_m \NR
}

In such case of insufficient measurements, possibly even with corruption of noise, do we have the knowledge of all \m {N_p} parameters?
Of course, more assumption must be made to make the question meaningful.
Any two vectors of parameters differing an element in the null space of the sensing matrix will produce the same measurement.

@@

\Result
{Definition}
{
\m {x \in \Mb {V}_{\Mb {K}} \SB {N_m}} is called \m {s}-sparse with support \m {\Mc {A}}, \m {s <N_m}, if there is \m {\Mc {A} \subset T \RB {N_m}} such that

\Disp { 
\NC x_{T\SB {N} -\Mc {A}}
=\NC \V {0} \NR
}
with
\Disp { 
\NC \# \Mc {A} \leq s. \NR
}
That is, only at most \m {s} components of \m {x} is nonzero.
}

\Result
{Definition}
{
Consider \m {P \in \Mb {M}_{\Mb {K}} \SB {N_m, N_p}}, with unity-\m {\ell_2}-norm columns.
For \m {s =1, \dots N_p}, we say that \m {P} satisfies the restricted isometry property (RIP) of sparsity \m {s} with respect to \m {0 \leq \d_s \leq 1}, if, for all \m {s}-sparse \m {\V {x} \in \Mb {V}_{\Mb {K}} \SB {N_p}}, for all \m {\Mc {T} \subset T\SB {N_m}} with \m {\#\{\Mc {T} \} \leq s},

\Disp {
\NC \NC \RB {1-\d_s} \VNm {V {x}}^2 \NR
\NC \leq \NC \VNm {P_{\Mc {T}} \V {x}} _2^2 \NR
\NC \leq \NC \RB {1+\d_s} \VNm {\V {x}} _2^2 \NR[+]
}
}

@@

Now, consider a linear transformation with noise corruption,

\Disp {
\NC \V {y} =\M {P} \V {h} + \V {z} \NR
}

where (w.l.o.g.) \m {z} is an i.i.d.\ normalized Gaussian vector.
How can we hope to estimate \m {h} when, in addition to insufficient observations, there are too few observations?

\Result
{Algorithm}
{
\startitemize[n]
\item Input \m {\M {P} \in \Mb {V}_\Mb {R} \SB {N_m, N_p}}, \m {\V {y} \in \Mb {V}_\Mb {R} \SB {N_m}}.
\item Find \m {\V {h} \in \Mb {V}_\Mb {R} \SB {N_m}} by
\Disp {
\NC \V {h}
= \NC \startcases
\NC \Min {\V {h}'} \quad \MC \VNm {\V {h}'} _1 \NR
\NC \Mr {subject} \; \Mr {to} \quad \MC \VNm {\M {P}^\Adj \RB {\M {P} \V {h} -\V {y}}} _\infty \leq \g \NR
\stopcases \NR
}
\item Output \m {\V {h}}.
}

@@

\Result
{Theorem}
{
Let each entry of random matrix \m {P \in \Mb {M}_\Mb {K} \SB {N_m, N_p}} be defined as i.i.d.\ Bernoulli with value \m {\pm 1/\R {N_m}} (that is, Rademacher distribution).
Then, with \m {0 <\e <1},

\Disp {
\NC \NC \Mb {P} \SB { \Nm {\VNm {P h} _2^2 -\VNm {h}_2^2} \geq \e \VNm {h} _2^2} \NR
\NC \leq \NC 2 \exp \SB {-n \RB {\F {\e ^2} {4} -\F {\e ^3} {6}} } \NR
}
}

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \m {0 <\d <1},

\Disp {
\NC M \geq 16s \log \RB {N/\d} \NR
}

Then OMP (Algorithm \_\_) recovers \m {x} completely, with overwhelming probability \m {1-\d}.
}

@@

\stopsection
\startsection [title={OMP used in Channel Sensing}]

For concreteness, let \m {\M {F}} be the precoder and \m {\M {W}} the combiner, and \m {\M {H}} the channel, and consider the noiseless case.
Let signal \m {\V {x}} be sent, and \m {\V {y}} be receiverd, that is

\Disp {
\NC \V {y} =\M {W} \M {H} \M {F} \V {x} \NR
}

% % % % % % % % % % % % % % % % % % % %

%I want to show the Kronecker Product identity listed on [Wikipedia](https://en.wikipedia.org/wiki/Kronecker_product):
%$$\begin{align}
%\mathrm{vec}(AXB)
%=(B^T \otimes A) \mathrm{vec}(X) \\ \tag{1}
%\end{align}$$
%Wikipedia does not cite references for the proof for (1), and I want to verify.
%Before the calculation, agree with some convention.
%Let us denote $a\; \mathrm{mod}\; b$ for the remainder of $a$ modulo $b$ (so that $9\; \mathrm{mod}\; 4 =1$).
%This is unlike the usual practice, but otherwise the expression gets too verbose.
%Moreover let us denote the $(i,j)$-th entry of $A$ to be $A_{i,j}$, and $i$-th entry of $v$ to be $v_{i}$.
%Also say that $A \in \mathbb{R}^{M \cdot N}$ if it is a $M$ by $N$ matrix, by slightly abusing the meaning of $\mathbb{R}$.
%If we stick to only addition and multiplication, once the proof works, it works for any field.
%
%Firstly, restate the formal definition of Kronecker product and vectorization, for later use.
%For $X' \in \mathbb{R}^{N_2 \cdot N_3}$
%$$\begin{align}
%(\mathrm{vec}(X'))_{m_1}
%=X'_{m_1\; \mathrm{mod}\; N_1, \lceil m_1/N_1 \rceil} \\ \tag{2}
%\end{align}$$
%
%For $A' \in \mathbb{R}^{N_1 \cdot N_2}, B' \in \mathbb{R}^{N_3 \cdot N_4}$,
%$$\begin{align}
%(A' \otimes B')_{m_1, m_2}
%=A'_{\lceil m_1/N_3 \rceil, \lceil m_2/N_4 \rceil}
%B'_{m_1\; \mathrm{mod}\; N_3, m_2\; \mathrm{mod}\; N_4} \\ \tag{3}
%\end{align}$$ 
%
%Now, let $A \in \mathbb{R}^{N_1 \cdot N_2},\; X \in \mathbb{R}^{N_2 \cdot N_3},\; B \in \mathbb{R}^{N_3 \cdot N_4},$,
%We try to evaluate lhs and rhs of (1).
%
%$$\begin{align}
%&(\mathrm{vec}(AXB))_{m_1} \\
%=&(AXB)_{m_1\; \mathrm{mod}\; N_1, \lceil m_1/N_1 \rceil} \\
%=&\sum_{n_2=1}^{N_2} \sum_{n_3=1}^{N_3}
%A_{m_1\; \mathrm{mod}\; N_1, n_2} X_{n_2, n_3} B_{n_3, \lceil m_1/N_1 \rceil} \\ \tag{4}
%\end{align}$$
%
%$$\begin{align}
%&((B^T \otimes A) \mathrm{vec}(X) )_{m_1} \\
%=&\sum_{m_2=1}^{N_2 N_3} (B^T \otimes A)_{m_1, m_2} \mathrm{vec}(X)_{m_2} \\
%=&\sum_{m_2=1}^{N_2 N_3} (B^T)_{\lceil m_1/N_1 \rceil, \lceil m_2/N_2 \rceil}
%A_{m_1\; \mathrm{mod}\; N_1, m_2\; \mathrm{mod}\; N_2} \mathrm{vec}(X)_{m_2} \\ 
%=&\sum_{m_2=1}^{N_2 N_3} B_{\lceil m_2/N_2 \rceil, \lceil m_1/N_1 \rceil}
%A_{m_1\; \mathrm{mod}\; N_1, m_2\; \mathrm{mod}\; N_2} X_{m_2\; \mathrm{mod}\; N_2, \lceil m_2/N_2 \rceil} \\ \tag{5}
%\end{align}$$ 
%
%It would seem that we are close, but it is not obvious that (4) and (5) are equal.
%Although $A$'s row index $m_1\; \mathrm{mod}\; N_1$ and $B$'s column index $\lceil m_1/N_1 \rceil$ agree, the other do not.
%It is suggestive that maybe if we "sum away" $n_2, n_3$, we might find them to agree, but $A,X,B$ are all free, and we have nothing to exploit to carry out that summation.

% % % % % % % % % % % % % % % % % % % %

\Result
{Definition.}
{
Define \m {\Mr {vec} \SB {\M {A}} \in \Mb {V}_{\Mb {K}} \SB {N_1, N_2}} to be the vectorization of \m {\M {A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}}.
Formally,
\Disp{
\NC \RB {\Mr{vec} \SB {\M{A}}} \DB {m_1}
=\NC \M{A} \DB {m_1\; \Mr{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR[+]
}
}

\Result
{Definition.}
{
For \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}} and \m {\M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}}, define the Kronecker product \m {\M{A} \otimes \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_1 N_3, N_2 N_4}} by
\Disp{
\NC \NC \RB {\M{A} \otimes \M{B}} \DB {m_1, m_2} \NR
\NC =\NC \M{A} \DB {\Fl{ m_1/N_3 }, \Fl{ m_2/N_4 }}
\M{B} \DB {m_1\; \Mr{Mod}\; N_3, m_2\; \Mr{Mod}\; N_4} \NR[+]
}
}

With (), scholars often exploit the relation

\Result
{Lemma.}
{
Suppose \m {\M{A} \in \Mb {M}_{\Mb {K}} \SB {N_1, N_2}, \M{X} \in \Mb {M}_{\Mb {K}} \SB {N_2, N_3}, \M{B} \in \Mb {M}_{\Mb {K}} \SB {N_3, N_4}},
Then
\Disp {
\NC \mathrm{vec} \RB {\M{A}\M{X}\M{B}}
= \NC \RB {\M{B}^\Tr \otimes \M{A}} \mathrm{vec} \SB {X} \NR
}
}

The proof is not particularly easy to find, and we show it here.
We thus verify that arbitrary components of lhs and rhs agree.
On one hand,

\Disp{
\NC \NC \RB {\Mr{vec} \SB {\M{A}\M{X}\M{B}}} \DB {m_1} \NR
\NC = \NC \RB {\M{A}\M{X}\M{B}} \DB {m_1\; \Mr{Mod}\; N_1, \Fl{ m_1/N_1 }} \NR
\NC = \NC \sum _{n_2=1} ^{N_2} \sum _{n_3=1} ^{N_3}
\M{A} \DB {m_1\; \Mr{Mod}\; N_1, n_2} \M{X} \DB {n_2, n_3} \M{B} \DB {n_3, \Fl{ m_1/N_1 }} \NR[+]
}

On the other hand,

\Disp{
\NC \NC \RB {\RB {\M{B}^\Tr \otimes \M{A}} \Mr{vec} \SB{\M{X}} } \DB {m_1} \NR
\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr \otimes \M{A}} \DB {m_1, m_2} \Mr{vec} \SB {\M{X}} \DB {m_2} \NR
\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \RB {\M{B}^\Tr} \DB {\Fl{ m_1/N_1 }, \Fl{ m_2/N_2 }}
\M{A} \DB {m_1\; \Mr{Mod}\; N_1, m_2\; \Mr{Mod}\; N_2} \Mr{vec} \SB {\M{X}} \DB {m_2} \NR 
\NC = \NC \sum _{m_2=1} ^{N_2 N_3} \M{B} \DB {\Fl{ m_2/N_2 }, \Fl{ m_1/N_1 }}
\M{A} \DB {m_1\; \Mr{Mod}\; N_1, m_2\; \Mr{Mod}\; N_2} \M{X} \DB {m_2\; \Mr{Mod}\; N_2, \Fl{ m_2/N_2 }} \NR[+]
}

In () and (), the row index of \m {\M{A}} and \m {\M{B}} already agree.
The key observation is that when \m {n_2} runs through \m {0, \dots, N_2-1} and \m {n_3} runs through \m {0, \dots, N_3-1}, it follows \m {n_2 n_3} runs through \m {0, \dots, N_2 N_3-1}.
We see two expressions are exactly the same, and we are done.
